%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
%墨尔本大学 super hack
  \cventry
    {Mentor} % Job title
    {Melbourne University Electrical Engineering Club} % Organization
    {Melbourne, Australia} % Location
    {Nov 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a mentor, help girls from schools across Victoria to compete in teams to solve engineering design challenges based on a real industry problem.}
        \item {They designed and built an autonomous robot to complete some specific tasks using the Arduino micro-controller and various electrical components ranging from IR-sensors to piezo buzzers.}
        \item {Those tasks include delivery cost and find a path in labyrinth.}
      \end{cvitems}
    }




%河南工业大学
  \cventry
    {Researcher} % Job title
    {Henan University of Technology} % Organization
    {Zhengzhou, China} % Location
    {Dec 2018 - Feb 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and program an Android application to recognize pests in food, based on deep learning and neural network.}
        \item {Using the camera in the granary, design an algorithm to measure the height of grain in the granary.}
        \item {Working in a team of 6 people. Meetings were held in 2pm every Tuesday afternoon, and Agile Management were applied during development.}
        \item {We successfully designed the algorithm, and built the Android application.}
      \end{cvitems}
    }

%---------------------------------------------------------
%郑州三晖电气
  \cventry
    {Software Engineer} % Job title
    {Zhengzhou Sanhui Electric Co., Ltd.} % Organization
    {Zhengzhou, China} % Location
    {June 2018 - Dec 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design the software to help the test engineer to test the circuit board conveniently and efficiently}
        \item {Written in C++, this software includes a user-friendly UI and a variety of different functions. For example, read the basic information about circuit, includes current, voltage and impedance. Write embedded programs into circuits.}
        \item {Program embedded system language based on C language to achieve some significant functions.}
        \item{Working in a team of 8 people. Meeting were held in 8pm every evening.}
      \end{cvitems}
    }

%---------------------------------------------------------


%---------------------------------------------------------
%西交利物浦 FYP
  \cventry
    {Researcher \& Core Member} % Job title
    {Xi’an Jiaotong Liverpool University} % Organization
    {Suzhou, China} % Location
    {Sep 2017 - June 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and program an application with user-interface based on Qt.}
        \item {The application can remote control the semiconductor analyzer Agilent B1500A. User can achieve all operations of Agilent B1500A in this application.}
      \end{cvitems}
    }




\end{cventries}
